Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-09 paper/main.tex
Minor spell corrections

\input{tables/supercop_sha256d}
Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. What we can see is that for lower lengths of data,
more of the candidates are faster than double \ac{SHA}-256. However, given the
practical situation that Tahoe-\ac{LAFS} is a filesystem, most files processed
will have be larger than the file sizes estimated here. Even though not all
hashing operations done in Tahoe are related to the file size, we expect that
only BLAKE, \ac{BMW}, Luffa, Shabal and SIMD will be able to outperform double
\ac{SHA}-256.

\section{Validity of \ac{SUPERCOP} results}
Although we believe the \ac{SUPERCOP} toolkit and results give good indication
of how fast the different candidate implementations are, we do have som
comments on it.

\paragraph{Implementations does not conform to \ac{NIST} specification} for
many of the candidates. By this we mean that there is no Update()-function
available for all implementation, and that \ac{SUPERCOP} only measures speed of
hashing full bytestrings. This is also a hasle for programmer who want to use
the implementations in \ac{SUPERCOP}

@@

\paragraph{Results are only valid for one specific computer}. The results we
used from \ac{SUPERCOP} are only valid for our specific computer, although it
gives an indication of which speeds can be achieved on similar computers, i.e.
32-bit. However to get a complete picture of the performance of the different
candidates one must look at different computers and architectures. This picture
might be obtained from looking at the results from all computeres measured by
\ac{SUPERCOP}.

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsitencies in the numbers, and try to explain them.
%
% Compare our results with general (supercop) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
% Time gain of removing ``double'' SHA-256. Double only in digest().
%
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compatability)
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently? Critisize
% ourselves.

>>>>

\input{tables/supercop_sha256d}
Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. What we can see is that for lower lengths of data,
more of the candidates are faster than double \ac{SHA}-256. However, given the
practical situation that Tahoe-\ac{LAFS} is a file system, most files processed
will have be larger than the file sizes estimated here. Even though not all
hashing operations done in Tahoe are related to the file size, we expect that
only BLAKE, \ac{BMW}, Luffa, Shabal and SIMD will be able to outperform double
\ac{SHA}-256.

\section{Validity of \ac{SUPERCOP} results}
Although we believe the \ac{SUPERCOP} toolkit and results give good indication
of how fast the different candidate implementations are, we do have some
comments on it.

\paragraph{Implementations does not conform to \ac{NIST} specification} for
many of the candidates. By this we mean that there is no Update()-function
available for all implementation, and that \ac{SUPERCOP} only measures speed of
hashing full byte strings. This is also a hassle for a programmer who want to
use the implementations in \ac{SUPERCOP}

@@

\paragraph{Results are only valid for one specific computer}. The results we
used from \ac{SUPERCOP} are only valid for our specific computer, although it
gives an indication of which speeds can be achieved on similar computers, i.e.
32-bit. However to get a complete picture of the performance of the different
candidates one must look at different computers and architectures. This picture
might be obtained from looking at the results from all computers measured by
\ac{SUPERCOP}.

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
% Time gain of removing ``double'' SHA-256. Double only in digest().
%
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compability)
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently? Criticize
% ourselves.
